---
title: "Data Science Batch 9 - Day 14 - Exploratory Data Analysis"
output: html_notebook
type: Assignment
name: Robby Ananta
---

## Load Library & Datasets

```{r}
library(tidyverse)

# run the following code (note that your datapath may different with this one)
data_house <- read.csv("C:/Users/robby/Desktop/R/house_ames.csv")
head(data_house)
```

HINT : you can check your data using panel on the right down search your data and click on it and select `import dataset` copy the data path

## 1. Data Types

```{r}
# change SalePrice datatype into double [score : 3]

SalePrice_double <- as.double(data_house$SalePrice)
head(SalePrice_double/ 1000)
is.double(SalePrice_double)
```

## 2. Finding Missing Values

```{r}
# count number of row
nr <- nrow(data_house)

# get number of missing values for each column
nmiss <- sapply(data_house, function(x) sum(is.na(x)))

# count missing percentage = number of missing values / total rows
missing_pct <-  nmiss / nr

# create dataframe
missing_data_pct <- as.data.frame(missing_pct)
colnames(missing_data_pct) <- c("missing_pct")

# filter out zero missing column
ress <- missing_data_pct %>% 
  filter(missing_pct > 0) %>% 
  arrange(desc(missing_pct))

# let's see the data
View(ress)
```

Run the chunk above, and answer the following questions:

1.  How many columns that have missing values ? [score: 2]

    19 kolom entries dari 81

2.  How many columns that have missing values more than 60% ? [score: 2]

    4 missing values: PoolQC, MiscFeature, Alley, Fence

3.  "Garage" related column have the same Null pct, can you guess what Null values in Garage column mean ? [score : 1]

    Tidak mempunyai Garage

## 3. Duplicates & Unique Values

```{r}
# distinct all column except Id
data_house %>% 
  distinct_at(vars(!Id))
```

1.  How many records that are duplicates ? [score: 2]

    Tidak ada duplicate records

## 4. Mistakes

```{r}
# Usually House is Built first, and then remodel, and then sold.
# find unusual house Id HINT : calculate difference of YearBuilt, YearRemodAdd,  and YrSold [score : 4]

data_house %>%
  count(YearBuilt, YearRemodAdd, YrSold, Id) %>%
  filter(YrSold < YearRemodAdd) %>%
  select(YearBuilt, YearRemodAdd, YrSold, Id)
```

1.  House's ID that Have unusual Sold Year is ... [score : 1]

    ID 524, yang di Built dan Sold pada tahun 2007, tetapi terjadi RemodAdd pada tahun 2008

## 5. Extreme Values

```{r}
# run the code below
ggplot(data_house) +
  geom_histogram(mapping = aes(x = SalePrice), bins=40, 
                 fill = "darkgreen", color = "white", linetype = "longdash")
```

After seeing the histogram, select values to be the filter values

```{r}
summary(data_house$SalePrice)

# combine verbs
filter_price <- data_house %>%
  filter(SalePrice > 500000 | SalePrice < 30000)%>%
  select(Id, LotArea, GarageArea, OverallQual, OverallCond, Neighborhood, SalePrice)

filter_price

# separate verbs
price_normal <- data_house %>%
  filter(SalePrice < 500000) %>%
  select(Id, LotArea, GarageArea, OverallQual, OverallCond, Neighborhood, SalePrice)

price_upnormal <- data_house %>%
  filter(SalePrice > 500000) %>%
  select(Id, LotArea, GarageArea, OverallQual, OverallCond, Neighborhood, SalePrice)

price_normal
price_upnormal
```

1.  How many house, sold with unusual price? [score : 2]

  # count(price_upnormal)
    
    hasilnya adalah 9 house sold

2.  in which neighborhood do the unusual house sold? [score : 3]

  # price_upnormal %>%
      count(Neighborhood)
    
    hasilnya adalah NoRidge: 3 house, NridgHt: 3 house, dan StoneBr: 3 house
    
